Analysis of NLA17 Dissolved Gas Indicator

### 2023-03-14 scripts/dgIndicatorAnalysis.Rmd
Pushing infrastructure for writing manuscript in .Rmd

```{r}
# about 15 minutes to load first time
# 6/7/21 <2 minutes
Sys.time()
load(paste0(localPath, "\\Environmental Protection Agency (EPA)\\ORD NLA17 Dissolved Gas - Documents\\inputData\\all_predictions.rda"))
Sys.time()
```

@@

```{r}
# 11 minutes on VM!
tic() # 7 minutes on laptop
all_predictions <- all_predictions %>%
  #filter(.draw == 1) %>% # testing
  mutate(area_km2 = area_ha / 100, # this works
         size_cat2 = ifelse(area_km2 < 0.1,
                            "<0.1",
                            ifelse(area_km2 >= 0.1 & area_km2 < 1,
                                   "0.1 - 1",
                                   ifelse(area_km2 >=1 & area_km2 <10,
                                          "0.1 - 1",
                                          ifelse(area_km2 >=10 & area_km2 <100,
                                                 "10 - 100",
                                                 ifelse(area_km2 >=100, 
                                                        ">100",
                                                        NA))))),
         size_cat2 = factor(size_cat2, ordered = TRUE, 
                            levels = c("<0.1", "0.1 - 1", "1 - 10", "10 - 100", ">100"))) %>%
  select(-area_km2)
toc()
gc() # this pushed memory up to 57.7 GB!  gc drops it to 32GB

@@

# point and linerange
all_predictions %>%
  group_by(WSA9, .draw) %>% # group by iteration
  #group_by(.draw) %>%
  summarise(mean_sat = mean(n2osat)) %>% # 500 means for each WSA9
  # now summarize to 1 statistic per WSA9
  summarise( estimate = round(median(mean_sat), 3), 
    LCL = round(quantile(mean_sat, probs = 0.025), 3),
    UCL = round(quantile(mean_sat, probs = 0.975), 3)) %>% 
  mutate(ecoregion = factor(WSA9)) %>%
  #mutate(type = "MR") %>%
  select(ecoregion, estimate, LCL, UCL) %>%
  mutate(ecoregion = fct_reorder(ecoregion, estimate)) %>%
  ggplot( aes( x = ecoregion, y = estimate ) ) +
  geom_point() +
  geom_linerange( aes( ymin = LCL, ymax = UCL)) +
  geom_hline(yintercept = 1, color='blue') +
  ylab("mean N2O saturation ratio") +
  coord_flip() + 
  theme_bw()
ggsave("output/figures/n2oSatRatioByEco.tiff")

@@

@@

# PLOT N2O SAT RATIO BY WSA9 AND SIZE------------------

# point and linerange
all_predictions %>%
  group_by(WSA9, size_cat, .draw) %>% # group by iteration
  #group_by(.draw) %>%
  summarise(mean_sat = mean(n2osat)) %>% # 500 means for each WSA9
  # now summarize to 1 statistic per WSA9
  summarise( estimate = round(median(mean_sat), 3), 
    LCL = round(quantile(mean_sat, probs = 0.025), 3),
    UCL = round(quantile(mean_sat, probs = 0.975), 3)) %>% 
  mutate(ecoregion = factor(WSA9)) %>%
  #mutate(type = "MR") %>%
  #select(ecoregion, estimate, LCL, UCL) %>%
  mutate(ecoregion = fct_reorder(ecoregion, estimate)) %>%
  ggplot( aes( x = size_cat, y = estimate ) ) +
  geom_point() +
  geom_linerange( aes( ymin = LCL, ymax = UCL)) +
  geom_hline(yintercept = 1, color='blue') +
  ylab("mean N2O saturation ratio") +
  coord_flip() + 
  theme_bw() +
  facet_wrap(~ecoregion)
ggsave("output/figures/n2oSatRatioByEcoAndSize.tiff")

@@

# Merge wind and all_predictions
tic() # 33 seconds
all_predictions <- full_join(all_predictions, wind, by = c(".row" = ".id")) # 40 seconds on laptop
toc()
dim(wind) # 465897
dim(all_predictions) #232948500, 500 observations for each lake
465897*500 #232948500

@@

# write reduced file to disk for less computationally intensive wrangling
all_predictions.w.small <- all_predictions.w %>% filter(.draw %in% 1:5)

save(all_predictions.w.small,
     file = paste0(Sys.getenv("USERPROFILE"),
                   "/Environmental Protection Agency (EPA)/",
                   "ORD NLA17 Dissolved Gas - Documents/",
                   "inputData/all_predictions_w_small.rda"))
```
### compared to literature and US GHG inventory
The distribution of N2O emission rates (mg N2O m-2 d-1) for one draw is very similar to that derived from a literature review of lake/reservoir emission rates (DelSontro et al), except for CPL which shows some exceedingly high rates.  Overall, our results look reasonable.

The total N2O flux from US lakes and reservoirs is minor compared to other anthropogenic N2O sources
```{r}
all_predictions.w %>% 
  filter(.draw == 1) %>% 
  ggplot(aes(x=e.n2o.mg.m2.d)) + 
  geom_density() +
  geom_rug() + 
  facet_wrap(~WSA9, scales = "free")

@@

# National scale number for lakess/reservoirs (this is is Gg)
national.lakes <- all_predictions %>% 
  group_by(.draw) %>% 
  summarise(total.n2o = sum(f.n2o.Mg.y)) %>% 
  summarise(Gg = round(mean(total.n2o), 3) / 1000, # divide by 1000 for Mg to Gg
            Gg_LCL = round(quantile(total.n2o, probs = 0.025), 3) / 1000, # divide by 1000 for Mg to Gg
            Gg_UCL = round(quantile(total.n2o, probs = 0.975), 3) / 1000) %>% # divide by 1000 for Mg to Gg
  mutate(source = "Lakes and Reservoirs")

@@

(national.lakes$Gg/sum(inventory$Gg)) * 1000 #0.7%
```

@@

```{r}
# density plot with RUG for one draw
all_predictions %>% filter(.draw == 1) %>% ggplot(aes(x=f.n2o.Mg.y)) + geom_density() +geom_rug() + facet_wrap(~WSA9, scales = "free")

# flux vs area for one draw
all_predictions.w %>% filter(.draw == 1) %>% ggplot(aes(y=f.n2o.Mg.y, x=area_ha)) + geom_point() + facet_wrap(~WSA9, scales = "free")

# bar plot by size category and ecoregion  
all_predictions.w %>% filter(.draw == 1) %>% group_by(WSA9, size_cat2) %>% summarise(total.n2o = sum(f.n2o.Mg.y)) %>% 
  ggplot(aes(x=size_cat2, y=total.n2o)) + geom_bar(stat = "identity") + facet_wrap(~WSA9, scales = "free")

# bar plot by size category with error
p <- all_predictions %>% 
  group_by(WSA9, .draw, size_cat2) %>% 
  summarise(total.n2o = sum(f.n2o.Mg.y)) %>% 
  group_by(WSA9, size_cat2) %>%
  summarise(post_med_fn2o = round(mean(total.n2o), 3), 
            LCL_fn2o = round(quantile(total.n2o, probs = 0.025), 3),
            UCL_fn2o = round(quantile(total.n2o, probs = 0.975), 3)) %>%
  ggplot(aes(x=size_cat2, y=post_med_fn2o)) + 
  geom_bar(stat = "identity") + 
  geom_errorbar(aes(x=size_cat2, ymin = LCL_fn2o, ymax = UCL_fn2o)) +
    xlab(expression(Lake~Size~Bin~(km^{2}))) +
  ylab(expression(Mg~N[2]*O~year^{-1})) +
  facet_wrap(~WSA9, scales = "free") +
  theme_bw()

@@

ggsave("output/figures/n2oFluxByLakeSizeWithError.tiff", g)

# bar plot by size category without error
p <- all_predictions.w %>% 
  group_by(WSA9, .draw, size_cat2) %>% 
  # tot x size x draw
  summarise(total.n2o = sum(f.n2o.Mg.y),
            obs = n()) %>% # number of lakes per WSA x size
  group_by(WSA9, size_cat2) %>%
  summarise(post_med_fn2o = round(mean(total.n2o), 3), # across draws
            LCL_fn2o = round(quantile(total.n2o, probs = 0.025), 3),
            UCL_fn2o = round(quantile(total.n2o, probs = 0.975), 3),
            obs = mean(obs)) %>% # obs is repeated across draws.  mean gives identity
  ggplot(aes(x=size_cat2, y=post_med_fn2o)) + 
  geom_bar(stat = "identity") + 
  xlab(expression(Lake~Size~Bin~(km^{2}))) +
  ylab(expression(Mg~N[2]*O~year^{-1})) +
  #scale_x_discrete(labels = c("min to 4", "4-10", "10-20", "20-50", ">50")) +
  #geom_errorbar(aes(x=size_cat, ymin = LCL_fn2o, ymax = UCL_fn2o)) +
  facet_wrap(~WSA9, scales = "free_y") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
  geom_text(aes(label = scales::comma(obs, accuracy = 1)), # comma for thousands separator, accurary for decimal points
            vjust = -0.5, size = 3) +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.2)))

@@

@@

>>>>

```{r}
# 2/8/2023 75sec on VM
tic()
load(paste0(localPath, "\\Environmental Protection Agency (EPA)\\ORD NLA17 Dissolved Gas - Documents\\inputData\\all_predictions.rda"))
toc()
```

@@

```{r}
# 4 minutes on VM. pushes memory up to 65GB [2/8/2023]
tic()
all_predictions <- all_predictions %>%
  #filter(.draw == 1) %>% # testing
  mutate(area_km2 = area_ha / 100, # this works
         size_cat2 = ifelse(area_km2 < 0.1,
                            "<0.1",
                            ifelse(area_km2 >= 0.1 & area_km2 < 1,
                                   "0.1 - 1",
                                   ifelse(area_km2 >=1 & area_km2 <10,
                                          "1 - 10",
                                          ifelse(area_km2 >=10 & area_km2 <100,
                                                 "10 - 100",
                                                 ifelse(area_km2 >=100, 
                                                        ">100",
                                                        NA))))),
         size_cat2 = factor(size_cat2, ordered = TRUE, 
                            levels = c("<0.1", "0.1 - 1", "1 - 10", "10 - 100", ">100"))) %>%
  select(-area_km2)
toc()
gc()

@@

# point and linerange: mean +/- 95%CI
all_predictions %>%
  group_by(WSA9, .draw) %>% # group by iteration
  #group_by(.draw) %>%
  summarise(mean_sat = mean(n2osat)) %>% # 500 means for each WSA9
  # now summarize to 1 statistic per WSA9
  summarise( estimate = round(median(mean_sat), 3), 
    LCL = round(quantile(mean_sat, probs = 0.025), 3),
    UCL = round(quantile(mean_sat, probs = 0.975), 3)) %>% 
  mutate(ecoregion = factor(WSA9)) %>%
  #mutate(type = "MR") %>%
  select(ecoregion, estimate, LCL, UCL) %>%
  mutate(ecoregion = fct_reorder(ecoregion, estimate)) %>%
  ggplot( aes( x = ecoregion, y = estimate ) ) +
  geom_point() +
  geom_linerange( aes( ymin = LCL, ymax = UCL)) +
  geom_hline(yintercept = 1, color='blue') +
  ylab("mean N2O saturation ratio") +
  coord_flip() + 
  theme_bw()
ggsave("output/figures/n2oSatRatioByEco.tiff")

# Box and whisker
all_predictions %>%
  filter(.draw == 1) %>%
  ggplot( aes( x = WSA9, y = n2osat ) ) +
  geom_boxplot() +
  ylab("mean N2O saturation ratio") +
  coord_flip() + 
  theme_bw()
ggsave("output/figures/n2oSatRatioByEcoBoxWhisker.tiff")

# point and linerange: mean AND MEDIAN.+/- 95%CI
all_predictions %>%
  group_by(WSA9, .draw) %>% # group by iteration
  #group_by(.draw) %>%
  summarise(mean_sat = mean(n2osat),
            median_sat = median(n2osat)) %>% # 500 means for each WSA9
  # now summarize to 1 statistic per WSA9
  summarise(estimate = round(median(mean_sat), 3), 
            LCL = round(quantile(mean_sat, probs = 0.025), 3),
            UCL = round(quantile(mean_sat, probs = 0.975), 3),
            estimate_md = round(median(median_sat), 3), 
            LCL_md = round(quantile(median_sat, probs = 0.025), 3),
            UCL_md = round(quantile(median_sat, probs = 0.975), 3)) %>% 
  mutate(ecoregion = factor(WSA9)) %>%
  #mutate(type = "MR") %>%
  #select(ecoregion, estimate, LCL, UCL) %>%
  mutate(ecoregion = fct_reorder(ecoregion, estimate)) %>%
  ggplot(aes( x = ecoregion, y = estimate )) +
  geom_point(color = "blue") +
  geom_linerange( aes( ymin = LCL, ymax = UCL), color = "blue") +
  geom_point(aes(x = ecoregion, y = estimate_md), color = "red") +
  geom_linerange( aes( ymin = LCL_md, ymax = UCL_md), color = "red") +
  geom_hline(yintercept = 1, linetype = "dashed") +
  ylab("mean N2O saturation ratio") +
  coord_flip() + 
  theme_bw()
ggsave("output/figures/n2oSatRatioByEcoMedianAndMean.tiff")

# density plots of predicted distribution, mean, and median
# using xlim to zoom in on values close to 1

dummy <- all_predictions %>%
  group_by(WSA9) %>%
  summarize(mean = mean(n2osat),
            median = median(n2osat)) %>%
  mutate(dens.med = c(2, 2.5, 2.3, 2.05, 1.75, 2.15, 2.2, 1.9, 1.9),
         dens.mean = c(.4, 1.9, 2, .6, .65, .45, 1.5, 1.45, 0.9),
         .draw = 1) # needed to match grouping aesthetic in ggplot call

tic() # 40 seconds for 100 draws
all_predictions %>%
  filter(.draw %in% 1:100) %>% # subset for practice
  #mutate(ecoregion = factor(WSA9)) %>%
  #mutate(ecoregion = fct_reorder(ecoregion, preds_sat)) %>%
  ggplot(aes(x = n2osat, group = .draw, color = .draw ) ) +
  geom_density(show.legend = FALSE) +
  geom_vline(xintercept = 1, color = "red") +
  geom_segment(data = dummy,
               aes(x = mean, xend = mean, y = 0,
                   yend = dens.mean),
               linetype = "solid") +
  geom_segment(data = dummy,
               aes(x = median, xend = median, y = 0,
                   yend = dens.med),
               linetype = "dashed") +
  ylab ("density") + 
  xlab(expression(N[2]*O~saturation~ratio)) +
  xlim(0,3) + # data range is 0-600, but sample max is 30
  facet_wrap(~WSA9) +
  theme_bw() +
  theme(legend.position = "none")
toc()
ggsave("output/figures/n2oSatRatioDensityByEcoWithMeanMedian.tiff", width = 8.5, height = 5)

@@

# PLOT N2O SAT RATIO BY WSA9 AND SIZE------------------
# point and linerange
all_predictions %>%
  group_by(WSA9, size_cat, .draw) %>% # group by iteration
  #group_by(.draw) %>%
  summarise(mean_sat = mean(n2osat)) %>% # 500 means for each WSA9
  # now summarize to 1 statistic per WSA9
  summarise( estimate = round(median(mean_sat), 3), 
    LCL = round(quantile(mean_sat, probs = 0.025), 3),
    UCL = round(quantile(mean_sat, probs = 0.975), 3)) %>% 
  mutate(ecoregion = factor(WSA9)) %>%
  #mutate(type = "MR") %>%
  #select(ecoregion, estimate, LCL, UCL) %>%
  mutate(ecoregion = fct_reorder(ecoregion, estimate)) %>%
  ggplot( aes( x = size_cat, y = estimate ) ) +
  geom_point() +
  geom_linerange( aes( ymin = LCL, ymax = UCL)) +
  geom_hline(yintercept = 1, color='blue') +
  ylab("mean N2O saturation ratio") +
  coord_flip() + 
  theme_bw() +
  facet_wrap(~ecoregion)
ggsave("output/figures/n2oSatRatioByEcoAndSize.tiff")

@@

@@

# Merge wind and all_predictions
tic() # 21 seconds on VM
all_predictions <- full_join(all_predictions, wind, by = c(".row" = ".id")) # 40 seconds on laptop
toc()
dim(wind) # 465897
dim(all_predictions) #232948500, 500 observations for each lake
465897*500 #232948500

@@

# # write reduced file to disk for less computationally intensive wrangling
# all_predictions.w.small <- all_predictions %>% filter(.draw %in% 1:5)
# 
# save(all_predictions.w.small,
#      file = paste0(Sys.getenv("USERPROFILE"),
#                    "/Environmental Protection Agency (EPA)/",
#                    "ORD NLA17 Dissolved Gas - Documents/",
#                    "inputData/all_predictions_w_small.rda"))
```
### compared to literature and US GHG inventory
The distribution of N2O emission rates (mg N2O m-2 d-1) for one draw is very similar to that derived from a literature review of lake/reservoir emission rates (DelSontro et al), except for CPL which shows some exceedingly high rates.  Overall, our results look reasonable.

The total N2O flux from US lakes and reservoirs is minor compared to other anthropogenic N2O sources
```{r}
all_predictions %>% 
  filter(.draw == 1) %>% 
  ggplot(aes(x=e.n2o.mg.m2.d)) + 
  geom_density() +
  geom_rug() + 
  facet_wrap(~WSA9, scales = "free")

@@

# National scale number for lakes/reservoirs (this is is Gg)
national.lakes <- all_predictions %>% 
  group_by(.draw) %>% 
  summarise(total.n2o = sum(f.n2o.Mg.y)) %>% 
  summarise(Gg = round(mean(total.n2o), 3) / 1000, # divide by 1000 for Mg to Gg
            Gg_LCL = round(quantile(total.n2o, probs = 0.025), 3) / 1000, # divide by 1000 for Mg to Gg
            Gg_UCL = round(quantile(total.n2o, probs = 0.975), 3) / 1000) %>% # divide by 1000 for Mg to Gg
  mutate(source = "Lakes and Reservoirs")

@@

(national.lakes$Gg/sum(inventory$Gg)) * 100 #0.07%
```

@@

```{r}
# EMISSION RATES---------
# density plot by ecoregion
all_predictions %>%
  filter(.draw %in% 1:10) %>% # subset for practice
  #mutate(ecoregion = factor(WSA9)) %>%
  #mutate(ecoregion = fct_reorder(ecoregion, preds_sat)) %>%
  ggplot(aes(x = e.n2o.mg.m2.d, group = .draw, color = .draw )) +
  geom_density(show.legend = FALSE) +
  #geom_vline(xintercept = 0, color = "red") +
  xlab(expression("N"[2]*"O"~ "emission"~ "rate" ~ "(mg" ~ N[2]*O ~ m^-2 ~ d^-1 ~ ")")) +
  #xlim(0,5) + # data range is 0-600, but sample max is 30
  facet_wrap(~WSA9, scales = "free") +
  theme_bw()

# density plot with RUG for one draw
all_predictions %>% 
  filter(.draw == 1) %>% 
  ggplot(aes(x=f.n2o.Mg.y)) + 
  geom_density() +
  geom_rug() + 
  facet_wrap(~WSA9, scales = "free")

# point and line range by size and ecoregion
all_predictions %>%
  group_by(WSA9, size_cat, .draw) %>% # group by iteration
  #group_by(.draw) %>%
  summarise(mean_e.n2o.mg.m2.d = mean(e.n2o.mg.m2.d)) %>% # 500 means for each WSA9 x size cat
  # now summarize to 1 statistic per WSA9
  summarise( estimate = round(median(mean_e.n2o.mg.m2.d), 3), 
    LCL = round(quantile(mean_e.n2o.mg.m2.d, probs = 0.025), 3),
    UCL = round(quantile(mean_e.n2o.mg.m2.d, probs = 0.975), 3)) %>% 
  mutate(ecoregion = factor(WSA9)) %>%
  #mutate(type = "MR") %>%
  #select(ecoregion, estimate, LCL, UCL) %>%
  mutate(ecoregion = fct_reorder(ecoregion, estimate)) %>%
  ggplot( aes( x = size_cat, y = estimate ) ) +
  geom_point() +
  geom_linerange( aes( ymin = LCL, ymax = UCL)) +
  geom_hline(yintercept = 0, color='blue') +
  ylab("mean N2O emission rate") +
  coord_flip() + 
  theme_bw() +
  facet_wrap(~ecoregion)
ggsave("output/figures/n2oEmissionRateBySizeEco.tiff", width = 7)

# FLUX-------------
# flux vs area for one draw
all_predictions %>% 
  filter(.draw == 1) %>% 
  ggplot(aes(y=f.n2o.Mg.y, x=area_ha)) + 
  geom_point() + 
  facet_wrap(~WSA9, scales = "free")

# flux by ecoregion
# point and linerange
all_predictions %>%
  group_by(WSA9, .draw) %>% # group by iteration
  #group_by(.draw) %>%
  summarise(mean_f = mean(f.n2o.Mg.y)) %>% # 500 means for each WSA9
  # now summarize to 1 statistic per WSA9
  summarise( estimate = round(median(mean_f), 3), 
    LCL = round(quantile(mean_f, probs = 0.025), 3),
    UCL = round(quantile(mean_f, probs = 0.975), 3)) %>% 
  mutate(ecoregion = factor(WSA9)) %>%
  #mutate(type = "MR") %>%
  select(ecoregion, estimate, LCL, UCL) %>%
  mutate(ecoregion = fct_reorder(ecoregion, estimate)) %>%
  ggplot( aes( x = ecoregion, y = estimate ) ) +
  geom_point() +
  geom_linerange( aes( ymin = LCL, ymax = UCL)) +
  geom_hline(yintercept = 0, color='blue') +
  ylab("mean N2O saturation ratio") +
  coord_flip() + 
  theme_bw()
ggsave("output/figures/n2oSatRatioByEco.tiff")

# point and line range by size and ecoregion
all_predictions %>%
  group_by(WSA9, size_cat, .draw) %>% # group by iteration
  #group_by(.draw) %>%
  summarise(mean_f.n2o.Mg.y = mean(f.n2o.Mg.y)) %>% # 500 means for each WSA9 x size cat
  # now summarize to 1 statistic per WSA9
  summarise( estimate = round(median(mean_f.n2o.Mg.y), 3), 
    LCL = round(quantile(mean_f.n2o.Mg.y, probs = 0.025), 3),
    UCL = round(quantile(mean_f.n2o.Mg.y, probs = 0.975), 3)) %>% 
  mutate(ecoregion = factor(WSA9)) %>%
  #mutate(type = "MR") %>%
  #select(ecoregion, estimate, LCL, UCL) %>%
  mutate(ecoregion = fct_reorder(ecoregion, estimate)) %>%
  ggplot( aes( x = size_cat, y = estimate ) ) +
  geom_point() +
  geom_linerange( aes( ymin = LCL, ymax = UCL)) +
  geom_hline(yintercept = 0, color='blue') +
  ylab("mean N2O flux") +
  coord_flip() + 
  theme_bw() +
  facet_wrap(~ecoregion, scales = "free")
ggsave("output/figures/n2oFluxBySizeEco.tiff", height = 5.4, width = 9.6)

# bar plot by size category and ecoregion  
all_predictions %>% 
  filter(.draw == 1) %>% 
  group_by(WSA9, size_cat2) %>% 
  summarise(total.n2o = sum(f.n2o.Mg.y)) %>% 
  ggplot(aes(x=size_cat2, y=total.n2o)) + 
  geom_bar(stat = "identity") + 
  facet_wrap(~WSA9, scales = "free")

# bar plot by size category with error
p <- all_predictions %>% 
  group_by(WSA9, .draw, size_cat2) %>% 
  summarise(total.n2o = sum(f.n2o.Mg.y)) %>% 
  group_by(WSA9, size_cat2) %>%
  summarise(post_med_fn2o = round(mean(total.n2o), 3), 
            LCL_fn2o = round(quantile(total.n2o, probs = 0.025), 3),
            UCL_fn2o = round(quantile(total.n2o, probs = 0.975), 3)) %>%
  ggplot(aes(x=size_cat2, y=post_med_fn2o)) + 
  geom_bar(stat = "identity") + 
  geom_errorbar(aes(x=size_cat2, ymin = LCL_fn2o, ymax = UCL_fn2o)) +
    xlab(expression(Lake~Size~Bin~(km^{2}))) +
  ylab(expression(Mg~N[2]*O~year^{-1})) +
  facet_wrap(~WSA9, scales = "free") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90))

@@

ggsave("output/figures/n2oFluxByLakeSizeWithError.tiff", g, width = 9.6, height = 5.4)

# bar plot by size category without error
p <- all_predictions %>% 
  group_by(WSA9, .draw, size_cat2) %>% 
  # tot x size x draw
  summarise(total.n2o = sum(f.n2o.Mg.y),
            obs = n()) %>% # number of lakes per WSA x size
  group_by(WSA9, size_cat2) %>%
  summarise(post_med_fn2o = round(mean(total.n2o), 3), # across draws
            LCL_fn2o = round(quantile(total.n2o, probs = 0.025), 3),
            UCL_fn2o = round(quantile(total.n2o, probs = 0.975), 3),
            obs = mean(obs)) %>% # obs is repeated across draws.  mean gives identity
  ggplot(aes(x=size_cat2, y=post_med_fn2o)) + 
  geom_bar(stat = "identity") + 
  xlab(expression(Lake~Size~Bin~(km^{2}))) +
  ylab(expression(Mg~N[2]*O~year^{-1})) +
  #scale_x_discrete(labels = c("min to 4", "4-10", "10-20", "20-50", ">50")) +
  #geom_errorbar(aes(x=size_cat, ymin = LCL_fn2o, ymax = UCL_fn2o)) +
  facet_wrap(~WSA9, scales = "free_y") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
  geom_text(aes(label = scales::comma(obs, accuracy = 1)), # comma for thousands separator, accurary for decimal points
            vjust = -0.5, size = 3) +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.2)))

@@

ecoreg_stats <- as.data.frame(ecoreg_stats)
class(ecoreg_stats)
str(ecoreg_stats) # WSA9 is a factor

@@

# Manuscript

Results and Discussion
In this study we present the first national-scale survey of N2O concentrations and emissions from lakes,  reservoirs, and ponds, hereafter referred to as waterbodies, in the conterminous U.S. (CONUS).  A generalized random-tessellation survey design (Stevens and Olsen, 2004) was used to select a spatially-balanced and representative sample of `r dg %>% distinct(site.id) %>% summarize(n = n()) %>% pull()` [weird, I have 1090, but NLA17 report says 1,005?] sites from CONUS waterbodies that are least 1 hectare in area, at least 1 meter deep, have at least 0.1 hectare of open water, and have a minimum residence time of one week (Figure 1).   Sample sites were distributed across all nine major CONUS ecoregions and varied widely in water chemistry, morphometry, watershed land-use, and climate (See NLA website for all data?). `r round(((dg %>% dplyr::filter(n2o.src.snk == "sink") %>% {nrow(.)} / dg %>% distinct(site.id) %>% {nrow(.)}) * 100), 1)` percent of the sampled waterbodies were undersaturated in N2O and were therefore functioning as N2O sinks.  We modeled the data using a bayesion hierchical approach and predicted the dissolved N2O concentration for all  224,916 CONUS waterbodies in the target population.  At the population level, `r all_predictions %>% group_by(.draw) %>% summarise(prop_sat = sum(n2osat < 1) / length(.row)) %>% summarise(estimate = round(median(prop_sat), 3) * 100) %>% pull()` percent (95% CI: `r all_predictions %>% group_by(.draw) %>% summarise(prop_sat = sum(n2osat < 1) / length(.row)) %>% summarise(LCL = round(quantile(prop_sat, probs = 0.025), 3) * 100) %>% pull()` - `r all_predictions %>% group_by(.draw) %>% summarise(prop_sat = sum(n2osat < 1) / length(.row)) %>% summarise(UCL = round(quantile(prop_sat, probs = 0.975), 3) * 100) %>% pull()`) of CONUS waterbodies were functioning as N2O sink.  The Western Mountains ecoregion had the smallest proportion of waterbodies functioning as N2O sinks (mean = `r all_predictions %>% group_by(WSA9, .draw) %>% summarise(prop_sat = sum(n2osat < 1) / length(.row)) %>% summarise(estimate = round(median(prop_sat), 3) * 100) %>% filter(WSA9 == "WMT") %>% select(estimate) %>% pull()`%, 95% CI: `r all_predictions %>% group_by(WSA9, .draw) %>% summarise(prop_sat = sum(n2osat < 1) / length(.row)) %>% summarise(LCL = round(quantile(prop_sat, probs = 0.025), 3) * 100) %>% filter(WSA9 == "WMT") %>% pull()` - `r all_predictions %>% group_by(WSA9, .draw) %>% summarise(prop_sat = sum(n2osat < 1) / length(.row)) %>% summarise(UCL = round(quantile(prop_sat, probs = 0.975), 3) * 100) %>% filter(WSA9 == "WMT") %>% pull()`) and the Northern Plains had the greatest (mean = `r all_predictions %>% group_by(WSA9, .draw) %>% summarise(prop_sat = sum(n2osat < 1) / length(.row)) %>% summarise(estimate = round(median(prop_sat), 3) * 100) %>% filter(WSA9 == "NPL") %>% select(estimate) %>% pull()`%, 95% CI: `r all_predictions %>% group_by(WSA9, .draw) %>% summarise(prop_sat = sum(n2osat < 1) / length(.row)) %>% summarise(LCL = round(quantile(prop_sat, probs = 0.025), 3) * 100) %>% filter(WSA9 == "NPL") %>% pull()` - `r all_predictions %>% group_by(WSA9, .draw) %>% summarise(prop_sat = sum(n2osat < 1) / length(.row)) %>% summarise(UCL = round(quantile(prop_sat, probs = 0.975), 3) * 100) %>% filter(WSA9 == "NPL") %>% pull()`)).

This survey design allows for extrapolation of the measurement results to all 224,916 CONUS waterbodies (this is from the 2017 NLA web report) in the target population.
